Open Data, Open Source and Open Standards in chemistry - The Blue Obelisk five years on

### 2011-04-14 paper.tex
Panton Principles

\section*{Open Data}
  \subsection*{Progress}
  \subsection*{Remaining challenges}

>>>>

\section*{Open Data}
  \subsection*{Progress}

A considerable stumbling block in advocating the release of scientific
data as Open Data has been how exactly to define Open. A major step
forward was the launch in 2010 of the Panton Principles for Open Data
in Science. This formalises the idea that Open Data maximises the
possibility of reuse and repurposing, the fundamental basis
of how science works. These principles recommend that published data
be licensed explicitly, and preferably under CC0 (Creative Commons "No
Rights Reserved"). This license allows others to use the data for any
purpose whatsoever without any barriers.
